### 2020-04-16 paper/UCOR.tex

The underlying framework is quite technical and requires one to handle
a computational model with what the original author %TODO: Insert reference
called Interactive Turing Machines and on top of this designed the
Universal Composability theorem \cite{UniversalComposability}. However, the most important part of
this framework is what is known as an {\bf Ideal Functionality}, which
can be thought of as a black box that fulfils some well-defined
functionality\cite{UniversalComposability}. The idea behind the \ac{UC} framework is then that we ought
to define a protocol which we must then prove simulates the ideal
functionality, so that distinguishing between the ideal functionality
and the real protocol becomes infeasible.

>>>>

The underlying framework is quite technical and requires one to handle
a computational model with what the original author %TODO: Insert reference
called Interactive Turing Machines and on top of this designed the
Universal Composability theorem \cite{UniversalComposability}. However, the most important part of
this framework is what is known as an \emph{ideal functionality}, which
can be thought of as a black box that fulfils some well-defined
functionality\cite{UniversalComposability}. The idea behind the \ac{UC} framework is then that we ought
to define a protocol which we must then prove simulates the ideal
functionality, so that distinguishing between the ideal functionality
and the real protocol becomes infeasible.
